Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-27 CAV 2025 TODO/Comparison.tex
scale
compar

The last case is the most problematic: 
Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$, because $cd >0$.
As for the case of $c>0, d>0$, opening $\ReLU(a)$ will have an impact on the value of $\hat{a}$,
at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{4}$ on the value of $b$.
However, as $d<0$, value of $\hat{b}$ needs to be minimized. That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$.
That is, the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
or $\Delta(b)<\frac{c}{2}$ otherwise (phase Id of ReLU), that is, $z$ will be modified by 
either 0 or $d \Delta(b)<\frac{cd}{2}$, as compared with $s_{FSB}(a)=\frac{cd}{4}$.

\begin{figure}[t!]
	\begin{tikzpicture}[scale=0.8, >=stealth]

>>>>

The last case is the most problematic: 
Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$, because $cd >0$.
As for the case of $c>0, d>0$, opening $\ReLU(a)$ will have an impact on the value of $\hat{a}$,
at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{2}$ on the value of $b$.
However, as $d<0$, value of $\hat{b}$ needs to be minimized. That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
or $\Delta(b)<\frac{c}{2}$ otherwise (phase Id of ReLU), that is, $z$ will be modified by 
either 0 or $d \Delta(b)<\frac{cd}{2}$, as compared with $s_{FSB}(a)=\frac{cd}{4}$.

\begin{figure}[t!]
	\begin{tikzpicture}[scale=1, >=stealth]
